Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/main-paper.tex
Shrink abstract and put fig in 1st page
Shrink intro
New paper structure with 1 section for each experiment
Add pero macro
Updates from Overleaf (#11)
small hack to reduce acknowledgements

\documentclass[runningheads,svgnames]{llncs}
%
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cleveref}
% \usepackage{tikz}
% \usepackage{nth}
% \usepackage{subcaption}
\usepackage{booktabs}
% \usepackage{array}
\usepackage{orcidlink}
\usepackage{subcaption} % Addition
\usepackage{multirow} % Addition
\usepackage{tabularx} % Addition
\usepackage{booktabs} % Addition
\usepackage{siunitx} % Addition
\usepackage{scalerel}
\usepackage{cleveref}

@@

% \renewcommand{\baselinestretch}{0.97}

@@

% Customize table rendering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.4}

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
% \thanks{%
% This work was supported by the French National Research Agency:
% Project SoDuCo, grant ANR-18-CE38-0013.% ???FIXME need acknowledgments for directory sources???
% }
}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{%
N. Abadie\inst{1}\orcidlink{0000-0001-8741-2398} \and
E. Carlinet\inst{2}\orcidlink{0000-0001-5737-5266} \and
J. Chazalon\inst{2}\orcidlink{0000-0002-3757-074X} \and
B. Duménieu\inst{3}\orcidlink{0000-0002-2517-2058}\\
{\footnotesize \emph{all authors contributed equally}}%
}
%
\authorrunning{N. Abadie et al.}
%
\institute{%
% 1
LASTIG, Univ. Gustave Eiffel, IGN-ENSG, F-94160 Saint-Mandé, France\\
\email{nathalie-f.abadie@ign.fr}%\\
% \url{https://www.umr-lastig.fr/nathalie-abadie/}%
\and
% 2
EPITA Research \& Development Laboratory (LRDE), Le Kremlin-Bicêtre, France\\
\email{\{edwin.carlinet,joseph.chazalon\}@lrde.epita.fr}%\\
%\url{https://lrde.epita.fr}
\and
% 3
CRH-EHESS, Paris, France\\
\email{bertrand.dumenieu@ehess.fr}%\\
% \url{http://crh.ehess.fr/index.php?5206}\\
\joseph{Je propose de supprimer les URLs.}%
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

% ---- Sections ----
\input{parts/10-introduction.tex}
\input{parts/20-related-work.tex}
\input{parts/30-dataset.tex}
\input{parts/40-ner-approaches.tex}
\input{parts/50-xp-setup.tex}
\input{parts/60-results.tex}
\input{parts/80-conclusion.tex}

\section*{Acknowledgments}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.
%
The authors want to thank S. Bacciochi and P. Cristofoli for helping to create the reference dataset, 
L. Morice for annotating data,
as well as G. Thomas, P. Abi Saad, R. Lelièvre, D. Mignon, T. Cavaciuti and P. Sadki for contributing to the annotation platform.
%
% Full names
% Stéphane Bacciochi
% Pascal Cristofoli
% Laureencia Morice
% Guillaume Thomas
% Paul Abi Saad
% Raphaël Lelièvre
% Dorian Mignon
% Thibault Cavaciuti
% Pierre Sadki

>>>>

\documentclass[runningheads,svgnames]{llncs}
%
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cleveref}
% \usepackage{tikz}
% \usepackage{nth}
\usepackage{booktabs}
% \usepackage{array}
\usepackage{orcidlink}
\usepackage{subcaption} % Addition
\usepackage{multirow} % Addition
\usepackage{tabularx} % Addition
\usepackage{siunitx} % Addition
\usepackage{scalerel}
\usepackage[inline,shortlabels]{enumitem}
\usepackage{xspace}

@@

% \renewcommand{\baselinestretch}{0.97}
\newcommand{\peroocr}{PERO OCR\xspace}

@@

% Customize table rendering
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.3}

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
% \thanks{%
% This work was supported by the French National Research Agency:
% Project SoDuCo, grant ANR-18-CE38-0013.% ???FIXME need acknowledgments for directory sources???
% }
}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{%
N. Abadie\inst{1}\orcidlink{0000-0001-8741-2398} \and
E. Carlinet\inst{2}\orcidlink{0000-0001-5737-5266} \and
J. Chazalon\inst{2}\orcidlink{0000-0002-3757-074X} \and
B. Duménieu\inst{3}\orcidlink{0000-0002-2517-2058}\\
{\footnotesize \emph{all authors contributed equally}}%
}
%
\authorrunning{N. Abadie et al.}
%
\institute{%
% 1
LASTIG, Univ. Gustave Eiffel, IGN-ENSG, F-94160 Saint-Mandé, France\\
\email{nathalie-f.abadie@ign.fr}%\\
% \url{https://www.umr-lastig.fr/nathalie-abadie/}%
\and
% 2
EPITA Research \& Development Laboratory (LRDE), Le Kremlin-Bicêtre, France\\
\email{\{edwin.carlinet,joseph.chazalon\}@lrde.epita.fr}%\\
%\url{https://lrde.epita.fr}
\and
% 3
CRH-EHESS, Paris, France\\
\email{bertrand.dumenieu@ehess.fr}%\\
% \url{http://crh.ehess.fr/index.php?5206}\\
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

% ---- Sections ----
\input{parts/10-introduction.tex}
\input{parts/20-related-work.tex}
\input{parts/30-dataset.tex}
\input{parts/40-ocr-bench.tex}
\input{parts/50-ner-xp1-training-set-size-and-pretraining.tex}
\input{parts/60-ner-xp2-pretraining-and-finetuning.tex}
\input{parts/80-conclusion.tex}

\bigskip
\noindent\textbf{Acknowledgments}\\
{
\footnotesize
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.
%
The authors want to thank S. Bacciochi and P. Cristofoli for helping to create the reference dataset, 
L. Morice for annotating data,
as well as G. Thomas, P. Abi Saad, R. Lelièvre, D. Mignon, T. Cavaciuti and P. Sadki for contributing to the annotation platform.
}
%
% Full names
% Stéphane Bacciochi
% Pascal Cristofoli
% Laureencia Morice
% Guillaume Thomas
% Paul Abi Saad
% Raphaël Lelièvre
% Dorian Mignon
% Thibault Cavaciuti
% Pierre Sadki
